%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

\newcommand{\LeftRight}[2]{%
  \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} p{0.75\linewidth} r}
    #1 & #2 \\
  \end{tabular*}
}

\newcommand{\Bitem}[1]{%
  \par\hangindent=2.4em\hangafter=1
  \noindent\hspace{1em}%
  \makebox[1.4em][l]{\raisebox{0.2ex}{\scriptsize$\bullet$}}#1\\[-2pt]%
}

\newcommand{\BitemEd}[1]{%
  \hangindent=2.4em\hangafter=1
  \hspace{1em}%
  \makebox[1.4em][l]{\raisebox{0.2ex}{\scriptsize$\bullet$}}%
  #1%
}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Annsh Navle} \\ \vspace{1pt}
    \small West Lafayette, IN $|$ 
    \small 765-682-3762 $|$ 
    \href{mailto:anavle@purdue.edu}{\underline{anavle@purdue.edu}} $|$
    %\href{https://annshnavle.dev/}{\underline{Website}} $|$ 
    \href{https://linkedin.com/in/annsh-navle}{\underline{LinkedIn}} $|$
    \href{https://github.com/Annsh-N}{\underline{GitHub}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
      \LeftRight{\textbf{Purdue University}}{May 2027} \\
      \LeftRight{B.S. in Computer Science, Physics (Double Major)}{West Lafayette, IN} \\
      \LeftRight{\BitemEd{\textbf{Relevant Coursework}: Data Structures and Algorithms, Software Engineering, Operating Systems, Computer Architecture, Embedded Systems}}{\textbf{GPA:} 3.84/4.00}
      \vspace{-6pt}

%-----------EXPERIENCE-----------
\section{Experience}

      \LeftRight{\textbf{Vice President Projects}}{\textbf{Feb. 2025 -- Present}}
      \LeftRight{\href{https://www.purduestack.org/}{\underline{Purdue Stack}}}{West Lafayette, IN} \\
        \Bitem{Leading end-to-end SDLC for 7 Agile teams, driving requirements, sprints, reviews, QA, and releases}
        \Bitem{Standardized delivery with CI/CD, PR gates, and release checklists to improve reliability and cadence}

      \vspace{7pt}  

      \LeftRight{\textbf{Software Engineer (Full Stack) Intern}}{\textbf{May 2025 -- Jul. 2025}}
      \LeftRight{Mindcraft Software Ltd.}{Mumbai, India} \\
        \Bitem{Developed Spring MVC backend for enterprise banking systems writing over 26,000 lines of production code}
        \Bitem{Created Angular 16 interface to extract insights from large document repositories using an internal LLM}
        \Bitem{Reduced employee onboarding time by 30\% by building JWT-secured Spring/Angular training portal}

        \vspace{7pt}  

      \LeftRight{\textbf{Backend Developer Intern}}{\textbf{Jun. 2024 -- Jul. 2024}}
      \LeftRight{Indepay}{Jakarta, Indonesia} \\
        \Bitem{Built and shipped Node.js REST APIs for mobile integration using JSON, contributing to 10\% user growth}
        \Bitem{Integrated 3 third-party financial APIs via OAuth2, adding token refresh, retries, and error handling}
        \Bitem{Improved observability and reliability with input validation, structured logging, and TCP/IP debugging}

      \vspace{7pt}  

      \LeftRight{\textbf{Research Developer}}{\textbf{Aug. 2023 - May. 2024}}
      \LeftRight{American Chemical Society (CAS)}{Remote} \\
        \Bitem{Developed Random Forest models using scikit-learn to predict chemical reactivity risks with 91\% accuracy}
        \Bitem{Automated data collection with Selenium pipelines and cron-driven scripts to expand ACS database by 20\%}
        \Bitem{Created Matplotlib dashboards to visualize classification accuracy, precision/recall metrics, error rates}  


%-----------PROJECTS-----------
\section{Projects}
    \LeftRight{\textbf{CS Alumni Dashboard $|$ React, Node.js, Express, PostgreSQL, Purdue SSO}}{\textbf{May 2025 - Aug. 2025}} \\
\Bitem{Built full-stack dashboard to analyze 3,000+ Purdue CS alumni by company, role, track and grad year}
\Bitem{Engineered secure SSO login, server-side filters, and modular admin tools with CSV upload and moderation}
\Bitem{Designed salary trend visualizations, internship outcome flows, exportable reports using D3.js and Chart.js}

\vspace{7pt}

\LeftRight{\textbf{PromptGate $|$ Cloudflare Workers, TypeScript, Durable Objects}}{\textbf{Jan. 2026}} \\
\Bitem{Built developer tool that compiles prompts with secret redaction and LLM-based semantic compression}
\Bitem{Reduced prompt tokens 30--50\% on noisy inputs and returned a report with cost and latency estimates}


\vspace{7pt}

\LeftRight{\textbf{AI PokerBot $|$ Python, TensorFlow, PyTorch, Numpy, Jupyter, React}}{\textbf{Aug. 2024 - Oct. 2024}} \\
\Bitem{Trained a reinforcement-learning poker agent using CFR Minimization, achieving 70\% win rate heads-up}
\Bitem{Built simulation and experiment pipeline (100,000+ runs) tracking convergence and regression testing}

%-----------CERTIFICATIONS-----------
\section{Certifications}

\LeftRight{\BitemEd{\textbf{Back-end Developer Professional (Meta)}}}{\textbf{Jan. 2025}}
\LeftRight{\BitemEd{\textbf{Machine Learning Engineer (Google)}}}{\textbf{Oct. 2024}}
\vspace{-12pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
     \Bitem{\textbf{Languages}{: Java, Python, Kotlin, Swift, C/C++/C\#, SQL, JavaScript, TypeScript, HTML, CSS, Bash}}
     \Bitem{\textbf{Frameworks/Libraries}{: Spring Boot, React, Node.js/Express, Angular, Flask, TensorFlow, OpenCV}}
     \Bitem{\textbf{Dev. Tools}{: VS Code, Cursor AI, GitHub Copilot, JupyterLab, Docker, Git, Postman, Agile/Scrum}}

\section{Interests}
    \Bitem{Fantasy Soccer, Poker, Sports Betting Markets, Video Editing, Weight Lifting}
     

%


%-------------------------------------------
\end{document}
